From OpenACC to OpenMP 4: \\ Toward Automatic Translation

### 2016-04-29 paper.tex
Start Related Work (Hernandez talk)

@@

\newpage

>>>>

\section{Related Work}

Most related to our work is a talk by Oscar Hernandez et al.\@ at
OpenMPCon~2015~\cite{hernandez,hernandezvideo}.  This talk describes the
salient differences between OpenACC~2.0 and OpenMP~4.0 and suggests a
(manual) procedure for porting code from OpenACC to OpenMP\@.  Their procedure
consists of five steps: removing constructs with no OpenMP counterparts (like
\emph{kernels}), translating data regions, translating data updates, translating
accelerator parallel regions, and adjusting function attribute specifiers.

@@

%\newpage
